The Effects of the NBA COVID Bubble on the NBA Playoffs

### 2022-02-01 Manuscript/NBABubbleAnalysis.Rmd
Update NBABubbleAnalysis.Rmd
Addressing reviewer 2 comment that we need to justify not using regression

>>>>

Regression was also considered, but it did not seem to add any additional useful
insight to answering the questions presented. Regression is a popular
tool in home court advantage studies, but as mentioned previously, this
study is very different from past studies. Rather than trying to prove the
existence of home court advantage, like many previous studies, this paper
was more interested in generating a clearer understanding of how home court
advantage effects each team. The most effective way to do that is hypothesis
testing to compare performance in the neutral bubble to previous years with
normal game conditions for both the home and away team. Another potential
benefit of regression would have been the ability to control for factors
like strength of opponent. However, we felt that strength of team was
already well enough controlled for by the fact that we focused on the
playoffs. The playoffs only include the strongest 16 of 30 teams, then
continue to remove the less competitive teams, so that the talent disparity
between teams is much smaller than regular season play where controlling for
opponent strength is likely more important.
